Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-29 paper.tex
barley section update

Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) was likely domesticated multiple times from wild subsp. \emph{spontaneum} roughly 8,000 to 10,000 BP.
There is clear evidence of one domestication center in the Fertile Crescent \cite{badr2000origin, Morrell2007}, and many have supported an additional eastern domestication event from subsp. \emph{spontaneum} var. \emph{agriocrithon} \cite{Morrell2007}, potentially in modern-day Tibet \cite{dai2012tibet}.
However, recent research \cite{pourkheirandish2018elucidation} has suggested that var. \emph{agriocrithon} is a misidentified intercultivar hybrid of domesticated 6-row landraces, which they deem \emph{pseudo-agriocrithon}, as opposed to \emph{eu-agriocrithon}, which are six-rowed wild relatives derived from two-rowed \emph{ssp. spontaneum}.
The non-brittle rachis mutations (\emph{btr1} and \emph{btr2}) appear to have arisen in populations from the Levant, whereas the two most common of four alleles conferring 6-rowed spike morphology (\emph{vrs1.a1} and \emph{vrs1.a4}) originated in \emph{eu-agriocrithon} populations in Central Asia (Turkmenistan and Uzbekistan, respectively).
These two key barley domestication traits were combined when \emph{vrs1.a1} and \emph{vrs1.a4} introgressed from \emph{eu-agriocrithon} into cultivated barleys in the Levant.

@@

>>>>

Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) was likely domesticated multiple times from wild subsp. \emph{spontaneum} roughly 8,000 to 10,000 BP.
There is clear evidence of one domestication center in the Fertile Crescent \cite{badr2000origin, Morrell2007}, and many have supported an additional eastern domestication event, potentially from \emph{subsp. spontaneum} east of the Zargos mountains \cite{Morrell2007} or from subsp. \emph{spontaneum} var. \emph{agriocrithon} in modern-day Tibet \cite{dai2012tibet}.
However, recent research \cite{pourkheirandish2018elucidation} suggests that Tibetan \emph{agriocrithon} is not a wild relative, but rather an intercultivar hybrid of domesticated landraces, casting doubt on the Tibetan domestication event from \emph{agriocrithon}.
%However, recent research \cite{pourkheirandish2018elucidation} has suggested that var. \emph{agriocrithon} is a misidentified intercultivar hybrid of domesticated 6-row landraces, which they deem \emph{pseudo-agriocrithon}, as opposed to \emph{eu-agriocrithon}, which are six-rowed wild relatives derived from two-rowed \emph{ssp. spontaneum}.
%The non-brittle rachis mutations (\emph{btr1} and \emph{btr2}) appear to have arisen in populations from the Levant, whereas the two most common of four alleles conferring 6-rowed spike morphology (\emph{vrs1.a1} and \emph{vrs1.a4}) originated in \emph{eu-agriocrithon} populations in Central Asia (Turkmenistan and Uzbekistan, respectively).
%These two key barley domestication traits were combined when \emph{vrs1.a1} and \emph{vrs1.a4} introgressed from \emph{eu-agriocrithon} into cultivated barleys in the Levant.

@@

Two key barley domestication traits are non-brittle rachis and 6-row spike morphology.
Haplotype analysis by Pourkheirandish and colleagues \cite{pourkheirandish2018elucidation} indicates that these two traits arose independently and were combined into domesticated barley when 6-row alleles (\emph{vrs1.a1} and \emph{vrs1.a4}) from \emph{spontaneum} introgressed into cultivated barleys from the Levant which harbored alleles for tough rachis (\emph{btr1} and \emph{btr2}).
